Marlowe: financial contracts on blockchain\thanks{This work is a part of the Cardano project, and is supported by IOHK}

### 2018-05-16 tex/paper.tex
Change tag version and fix two typos

%
%
% Title portion. Note the short title for running heads
\title {Marlowe: financial contracts on blockchain\thanks{IOHK}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Pablo Lamela Seijas\orcidID{0000-0002-1730-1219}\\
\and Simon Thompson\orcidID{0000-0002-2350-301X}}
%
\authorrunning{P. Lamela Seijas and S. Thompson}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Kent, Canterbury, CT2 7NF, Kent (UK)}
\email{\{pl292,s.j.thompson\}@kent.ac.uk}

@@

The paper describes version 1.2 of Marlowe, and it should be seen as a work in progress. We have designed it to provide 
financial contracts in Cardano, but also in order to start to answer the twin questions of what smart contracts will 
look like in Cardano, and how those contracts will be implemented in the overall system.

@@

\medskip
\noindent
In this section we look at existing work on smart contracts and blockchains in general, before exploring the rationale 
for building the Marlowe language.

@@

In designing, Marlowe we have chosen a number of options; this description applies to Marlowe version 1.2

@@

We have given a concrete model and DSL, namely Marlowe version 
1.2\footnote{\url{https://github.com/input-output-hk/scdsl/releases/tag/v1.2}}.
In this section we examine how the model can be extended, how contacts can be analysed, reflect on different design 
decisions that might be made and discuss some aspects of the implementation of Marlowe within a blockchain environment.

@@

We plan to continue the work with Marlowe in a number of directions. First, we need to sign off a definition of the 
language, as the current status of Marlowe 1.2 is that of a proposal.

>>>>

%
%
% Title portion. Note the short title for running heads
\title {Marlowe: financial contracts on blockchain\thanks{This work is a part of the Cardano project, and is
supported by IOHK}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Pablo Lamela Seijas\orcidID{0000-0002-1730-1219}\\
\and Simon Thompson\orcidID{0000-0002-2350-301X}}
%
\authorrunning{P. Lamela Seijas and S. Thompson}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Kent, Canterbury, CT2 7NF, Kent (UK)}
\email{\{pl292,s.j.thompson\}@kent.ac.uk}

@@

The paper describes version 1.3 of Marlowe, and it should be seen as a work in progress. We have designed it to provide 
financial contracts in Cardano, but also in order to start to answer the twin questions of what smart contracts will 
look like in Cardano, and how those contracts will be implemented in the overall system.

@@

\medskip
\noindent
In this section, we look at existing work on smart contracts and blockchains in general, before exploring the rationale 
for building the Marlowe language.

@@

In designing Marlowe, we have chosen a number of options; this description applies to Marlowe version 1.3.

@@

We have given a concrete model and DSL, namely Marlowe version 
1.3\footnote{\url{https://github.com/input-output-hk/scdsl/releases/tag/v1.3}}.
In this section we examine how the model can be extended, how contacts can be analysed, reflect on different design 
decisions that might be made and discuss some aspects of the implementation of Marlowe within a blockchain environment.

@@

We plan to continue the work with Marlowe in a number of directions. First, we need to sign off a definition of the 
language, as the current status of Marlowe 1.3 is that of a proposal.
